Lake Photic Zone Temperature accross the Conterminous United States

### 2019-04-02 manuscript/manuscript.Rmd
small changes

```{r setup, include=FALSE}
source(here::here("R/functions.R"), encoding = "UTF-8")
opts_chunk$set(echo = TRUE, fig.width=6, fig.height=5)
tab_num <- captioner(prefix = "Table")
fig_num <- captioner(prefix = "Figure")
options(scipen = 2, digits = 5)
```

```{r analysis, include=FALSE}
#got to figure out path stuff before render.
source(here::here("R/data_available.R"), encoding = "UTF-8") 
source(here::here("R/summary_stats.R"), encoding = "UTF-8")  
source(here::here("R/figures.R"), encoding = "UTF-8")
```

>>>>

```{r setup, include=FALSE, eval=FALSE}
source(here::here("R/functions.R"), encoding = "UTF-8")
opts_chunk$set(echo = TRUE, fig.width=6, fig.height=5)
tab_num <- captioner(prefix = "Table")
fig_num <- captioner(prefix = "Figure")
options(scipen = 2, digits = 5)
```

```{r analysis, include=FALSE, eval=FALSE}
#got to figure out path stuff before render.
source(here::here("R/data_available.R"), encoding = "UTF-8") 
source(here::here("R/summary_stats.R"), encoding = "UTF-8")  
source(here::here("R/figures.R"), encoding = "UTF-8")
```
